Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary

### 2020-09-08 scripts/MouseSexDiffVar_05_2020.Rmd
Fixed some input data problems for code. Class was character when should be numeric. Not sure why this issues popped up as it was never a problem for me in the past

overall4.female.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)

overall4.female.sigS$label <- "CI not overlapping zero"

@@

>>>>

overall4.female.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% select(GroupingTerm, parameter, value, ci.low, ci.high)
overall4.female.sigS <- overall4.female.sigS %>%
                          mutate(value = as.numeric(value),
                                 ci.low = as.numeric(ci.low),
                                 ci.high = as.numeric(ci.low))
overall4.female.sigS$label <- "CI not overlapping zero"

@@

overall4.male.sigS <- rbind(lnCVR.ci, lnVR.ci, lnRR.ci) %>% 
                      select(GroupingTerm, parameter, value, ci.low, ci.high) %>%
                      mutate(value = as.numeric(value), ci.low = as.numeric(ci.low), ci.high = as.numeric(ci.high))
